### 2021-11-01 content/80.formal-definition.tex
section reference for appendix
section reference

@@

Notable from this triple-like formalization is that a RO-Crate $R$ is fully represented as a tree at depth 2 helped by the use of $𝕀𝕣𝕚$ nodes. For instance the aggregation from the root entity $hasPart(\texttt{…interviews/>})$ is at same level as the data entity’s property $license(\texttt{…CC-BY-NC-4.0>})$ and that contextual entity’s attribute $ name(\text{…Non Commercial 4.0”})$. As shown in section RO-Crate JSON-LD, the RO-Crate Metadata File serialization is an equivalent shallow tree, although at depth 3 to cater for the JSON-LD preamble of \texttt{"@context"} and \texttt{"@graph"}.

>>>>

\label{sec:formaldefinition}

@@

Notable from this triple-like formalization is that a RO-Crate $R$ is fully represented as a tree at depth 2 helped by the use of $𝕀𝕣𝕚$ nodes. For instance the aggregation from the root entity $hasPart(\texttt{…interviews/>})$ is at same level as the data entity’s property $license(\texttt{…CC-BY-NC-4.0>})$ and that contextual entity’s attribute $ name(\text{…Non Commercial 4.0”})$. As shown in section \ref{sec:jsonld}, the RO-Crate Metadata File serialization is an equivalent shallow tree, although at depth 3 to cater for the JSON-LD preamble of \texttt{"@context"} and \texttt{"@graph"}.
